\section*{\centering BIBLIOGRAPHIE}
\addcontentsline{toc}{section}{BIBLIOGRAPHIE}

\begin{enumerate}

\item Quigley, M., Conley, K., Gerkey, B., Faust, J., Foote, T., Leibs, J.,
Wheeler, R., \& Ng, A. Y. (2009).
\textit{ROS: An Open-Source Robot Operating System}.
Proceedings of the ICRA Workshop on Open Source Software, Kobe, Japan.

\item Thrun, S., Burgard, W., \& Fox, D. (2005).
\textit{Probabilistic Robotics}.
MIT Press.

\item Siegwart, R., Nourbakhsh, I. R., \& Scaramuzza, D. (2011).
\textit{Introduction to Autonomous Mobile Robots} (2nd ed.).
MIT Press.

\item Siciliano, B., \& Khatib, O. (2016).
\textit{Springer Handbook of Robotics} (2nd ed.).
Springer.

\item OASIS. (2014).
\textit{MQTT Version 3.1.1 Plus Errata 01}.
OASIS Standard.

\item Fielding, R. T. (2000).
\textit{Architectural Styles and the Design of Network-Based Software Architectures}.
Doctoral dissertation, University of California, Irvine.

\item Gamma, E., Helm, R., Johnson, R., \& Vlissides, J. (1994).
\textit{Design Patterns: Elements of Reusable Object-Oriented Software}.
Addison-Wesley.

\item ISO 9241-210. (2019).
\textit{Ergonomics of Human-System Interaction — Part 210: Human-centred Design for Interactive Systems}.
International Organization for Standardization.

\item Object Management Group (OMG). (2021).
\textit{Unified Modeling Language (UML), Version 2.5.1}.

\item HESTIM Engineering \& Business School. (2026).
\textit{Development of a Custom Interaction and Control System for an Android-Based Service Robot}.
Document de sujet de stage. Encadrant : M. Sridath Tula.

\end{enumerate}